Time for a rethink: time sub-sampling methods in disparity-through-time analyses

### 2018-02-05 manuscript/time-slice.tex
Edits to fig 3 legend

% Plots showing the differences
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-peaks-epoch-revision.pdf}
    \caption[Timing of peak disparity for four example datasets.]
    {Timing of peak disparity.
    Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Pink points represent time binning methods, green points are time-slices with a punctuated model of evolution (`proximity' method), and blue points are time-slices with a gradual model of evolution (`gradual splits' method). 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic epochs. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic epochs in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic epochs in the time frame of the dataset. 
    For time bins there are two points indicating the maximum and minimum ages of the time bin within which peak disparities appeared.
    The four datasets are on separate rows, from top to bottom these are Beck2014, Brusatte2014, Bapst2016 and Wright2017 (see Table \ref{table:datasets} for details).
    Results for stratigraphic stages, and for other time-slicing methods, are in the Supporting Information Appendix S2: Figures A3-A4.}
    \label{figure:peak1}
\end{figure}

>>>>

% Plots showing the differences
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-peaks-epoch-revision.pdf}
    \caption[Timing of peak disparity for four example datasets.]
    {Timing of peak disparity.
    Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Green points represent time binning methods, blue points are time-slices with a punctuated model of evolution (`proximity' method), and purple points are time-slices with a gradual model of evolution (`gradual splits' method). 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic epochs. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic epochs in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic epochs in the time frame of the dataset. 
    For time bins there are two points indicating the maximum and minimum ages of the time bin within which peak disparities appeared.
    The four dataset names are on the first plot for each dataset (see Table \ref{table:datasets} for details).
    Results for stratigraphic stages, and for other time-slicing methods, are in the Supporting Information Appendix S2: Figures A3-A4.}
    \label{figure:peak1}
\end{figure}
